---
title: "Inference in the sparse ER model with covariates -- Model 1"
author: "Stefan Stein"
date: "25/05/2020"
output: 
  pdf_document:
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(kableExtra)
library(matrixStats)
library(tidyverse)
```



## Model setup


```{r, include=FALSE}
M <- 1000
sample_sizes <- c(300,500,800,1000)
p <- 20
subdirectory <- "Results"
path <- paste0(getwd(),"/", subdirectory)

### Results

get_files <- function(sample_size){
  list.files(path = path,
             pattern = paste0("*", sample_size, "_gamma_inference.csv"), full.names = T)%>%
    sapply(read_csv, col_names = FALSE, simplify = FALSE) %>%
    bind_rows()%>%
    setNames(c(paste0("Standardized_gamma_error_",1:p),
               paste0("CI_length_",1:p), 
               paste0("Coverage_",1:p)))%>%
    mutate(n = sample_size,)%>%
    select(n, everything())%>%
    mutate(gamma_l1 = list.files(path = path,
                                 pattern = paste0("*", sample_size, "_gamma_l1_*"), full.names = T)%>%
             sapply(read_csv, col_names = FALSE, simplify = FALSE) %>%
             bind_rows()%>%
             pull(X1))%>%
    mutate(gamma_l2 = list.files(path = path,
                                 pattern = paste0("*", sample_size, "_gamma_l2_*"), full.names = T)%>%
             sapply(read_csv, col_names = FALSE, simplify = FALSE) %>%
             bind_rows()%>%
             pull(X1))%>%
    mutate(mu_error = list.files(path = path,
                                 pattern = paste0("*", sample_size, "mu_error*"), full.names = T)%>%
             sapply(read_csv, col_names = FALSE, simplify = FALSE) %>%
             bind_rows()%>%
             pull(X1)%>%
             abs())%>%
    cbind(list.files(path = path,
                     pattern = paste0("*", sample_size, "_network_summaries*"), full.names = T)%>%
            sapply(read_csv, col_names = FALSE, simplify = FALSE) %>% 
            bind_rows()%>%
            setNames(c("unique_degrees", "total_degree", 
                       "edge_density", 
                       "min_prob", "1st_Qu_prob", "median_prob",
                       "mean_prob", "3rd_Qu_prob", "max_prob")))
}


results <- lapply(sample_sizes, get_files)%>%
  bind_rows()

```


## Network summaries

```{r, echo=FALSE}
knitr::kable(results%>%group_by(n)%>%
               summarise(median_edge_density=median(edge_density),
                         median_min_prob = median(min_prob),
                         median_max_prob = median(max_prob),
                         median_avg_prob = median(mean_prob)),
             caption = "Network density accross different n",
             col.names = c("n", "Median edge density", "Median \nmin probability",
                           "Median \nmax probability",
                           "Median \navg probability"),
             booktabs = TRUE)%>%
    kable_styling(latex_options = "hold_position")
```



## Inference

```{r, include=FALSE}

## Coverage summaries

coverage <- results%>%
  select(n, contains("Coverage"))%>%
  group_by(n)%>%
  summarise_all(mean)%>%
  ungroup()%>%
  select(-n)%>%
  as.matrix()%>%
  rowMedians()

CI_lengths <- results%>%
  select(n, contains("CI_length"))%>%
  group_by(n)%>%
  summarize_all(median)%>%
  ungroup()%>%
  select(-n)%>%
  as.matrix()%>%
  rowMedians()

standardized_gamma <- results%>%
  select(n, contains("Standardized"))%>%
  group_by(n)%>%
  summarize_all(median)%>%
  ungroup()%>%
  select(-n)%>%
  as.matrix()%>%
  rowMedians()

inference_results <- tibble(n = sample_sizes,
                                Coverage = coverage,
                                CI_length = CI_lengths,
                                Standardized_gamma = standardized_gamma)

```


In each run I calculate the standardized $\gamma$-values
\[
  \sqrt{\binom{n}{2}}\frac{\hat \gamma_k - \gamma_{0,k}}{\sqrt{\hat \Theta_{k,k}}}, \ k = 1,2.
\]
Asymptotically this should follow a $\mathcal{N}(0,1)$ distribution and we take a look at the corresponding histogram.

I also calculate confidence intervals for our $\gamma$ estimates. I take a straightforward approach and calculate the confidence intervals at the $95\%$ level as
\[
  CI_k = \left(\hat \gamma_k - 1.96 \times \sqrt{\frac{\hat \Theta_{k,k}}{\binom{n}{2}}}, \hat \gamma_k + 1.96 \times \sqrt{\frac{\hat \Theta_{k,k}}{\binom{n}{2}}} \right), \ k = 1,2.
\]


The results for the calibrated model are summarized in the tables below.

```{r, echo=FALSE}
knitr::kable(inference_results,
             caption = "Inference results for gamma",
             col.names = c("n", "Empirical coverage", "Median length CI", "Median Error"),
             booktabs = TRUE)%>%
  kable_styling(latex_options = "hold_position")
```
