---
title: "Simulation results -- Model 1"
author: "Stefan Stein"
date: "09/03/2020"
output: 
  pdf_document:
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(kableExtra)
library(tidyverse)
```


## Inference

```{r, include=FALSE}
M <- 1000
sample_sizes <- c(300,500,800,1000)
subdirectory <- "simulation_results"
path <- paste0(getwd(),"/", subdirectory)

### Results

get_files <- function(sample_size){
  list.files(path = path,
             pattern = paste0("*", sample_size, "_FL_beta*"), full.names = T)%>%
    sapply(read_csv, col_names = FALSE, simplify = FALSE) %>%
    bind_rows()%>%
    setNames("beta_mae")%>%
    mutate(n = sample_size,
           penalty = "pre-determined")%>%
    select(n, penalty, everything())%>%
    mutate(beta_mae = beta_mae / n)%>%
    mutate(mu_abs = list.files(path = path,
                               pattern = paste0("*", sample_size, "_FL_mu_error.csv*"), full.names = T)%>%
             sapply(read_csv, col_names = FALSE, simplify = FALSE) %>%
             bind_rows()%>%
             pull(X1)%>%abs())%>%
    mutate(gamma_l1 = list.files(path = path,
                                 pattern = paste0("*", sample_size, "_FL_gamma_l1*"), full.names = T)%>%
             sapply(read_csv, col_names = FALSE, simplify = FALSE) %>%
             bind_rows()%>%
             pull(X1)%>%abs())%>%
    cbind(list.files(path = path,
                     pattern = paste0("*", sample_size, "_FL_gamma_inference*"), full.names = T)%>%
            sapply(read_csv, col_names = FALSE, simplify = FALSE) %>% 
            bind_rows()%>%
            setNames(c("Standardized_gamma_1", "Standardized_gamma_2", 
                       "Coverage_gamma_1", "Length_CI_gamma_1",
                       "Coverage_gamma_2", "Length_CI_gamma_2")))%>%
    bind_rows(
      list.files(path = path,
                 pattern = paste0("*", sample_size, "_IC_matrix*"), full.names = T)%>%
        sapply(read_csv, col_names = FALSE, simplify = FALSE) %>% 
        bind_rows()%>%
        select(X7, X25, X28)%>%
        setNames(c("beta_mae", "mu_abs", "gamma_l1"))%>%
        mutate(mu_abs = abs(mu_abs),
               n = sample_size,
               penalty = "BIC")%>%
        select(n, penalty, everything())%>%
        cbind(list.files(path = path,
                         pattern = paste0("*", sample_size, "_BIC_gamma_inference*"), full.names = T)%>%
                sapply(read_csv, col_names = FALSE, simplify = FALSE) %>% 
                bind_rows()%>%
                setNames(c("Standardized_gamma_1", "Standardized_gamma_2", 
                           "Coverage_gamma_1", "Length_CI_gamma_1",
                           "Coverage_gamma_2", "Length_CI_gamma_2")))
    )
  
  
  
}


results <- lapply(sample_sizes, get_files)%>%
  bind_rows()

```



```{r, include=FALSE}

## Coverage summaries

inference_results <- results%>%group_by(n, penalty)%>%
  summarise(Coverage_gamma_1 = sum(Coverage_gamma_1)/M,
            Coverage_gamma_2 = sum(Coverage_gamma_2)/M,
            median_length_CI_1 = median(Length_CI_gamma_1),
            median_length_CI_2 = median(Length_CI_gamma_2),
            mean_standardized_1 = mean(Standardized_gamma_1),
            mean_standardized_2 = mean(Standardized_gamma_2),
            median_standardized_1 = median(Standardized_gamma_1),
            median_standardized_2 = median(Standardized_gamma_2))%>%
  arrange(desc(penalty))

```


In each run we calculate the standardized $\gamma$-values
\[
  \sqrt{\binom{n}{2}}\frac{\hat \gamma_k - \gamma_{0,k}}{\sqrt{\hat \Theta_{k,k}}}, \ k = 1,2.
\]
Asymptotically this should follow a $\mathcal{N}(0,1)$ distribution and we take a look at the corresponding histogram.

We also calculate confidence intervals for our $\gamma$ estimates. I take a straightforward approach and calculate the confidence intervals at the $95\%$ level as
\[
  CI_k = \left(\hat \gamma_k - 1.96 \times \sqrt{\frac{\hat \Theta_{k,k}}{\binom{n}{2}}}, \hat \gamma_k + 1.96 \times \sqrt{\frac{\hat \Theta_{k,k}}{\binom{n}{2}}} \right), \ k = 1,2.
\]


The results for the calibrated model are summarized in the tables below.

```{r, echo=FALSE}
knitr::kable(inference_results[,c(1,3,5,7,9)],
      caption = "Inference results for gamma 1",
      col.names = c("n", "Empirical coverage", "Median length CI", 
                    "Mean", "Median"),
      booktabs = TRUE)%>%
  pack_rows("Pre-determined lambda", 1, length(sample_sizes))%>%
  pack_rows("BIC", length(sample_sizes)+1, 2*length(sample_sizes))%>%
  kable_styling(latex_options = "hold_position")

```

```{r, echo=FALSE}
knitr::kable(inference_results[,c(1,4,6,8,10)],
      caption = "Inference results for gamma 2",
      col.names = c("n", "Empirical coverage", "Median length CI", 
                    "Mean", "Median"),
      booktabs = TRUE)%>%
  pack_rows("Pre-determined lambda", 1, length(sample_sizes))%>%
  pack_rows("BIC", length(sample_sizes)+1, 2*length(sample_sizes))%>%
  kable_styling(latex_options = "hold_position")

```

## Consistency

We calculate the mean absolute error for $\beta$, the absolute error for $\mu$ and the $\ell_1$-error for $\gamma$ and look at the corresponding boxplots comparing the pre-determined choice of $\lambda$ with the choice made by $BIC$.


```{r, echo=FALSE}
ggplot(data = results, mapping = aes(x = as.factor(n), y = beta_mae))+
  geom_boxplot(aes(color = penalty))+
  labs(title = paste("MAE for beta: BIC and pre-determined lambda \n(log-scale) for", M , "repetitions."),
       x = "Network size n",
       y = "MAE")+
  scale_y_log10()
```

```{r, echo=FALSE}
ggplot(data = results, mapping = aes(x = as.factor(n), y = mu_abs))+
  geom_boxplot(aes(color = penalty))+
  labs(title = paste("Absolute error for mu: BIC and pre-determined lambda \n for", M, "repetitions."),
       x = "Network size n",
       y = "Absolute error")

```



```{r, echo=FALSE}
ggplot(data = results, mapping = aes(x = as.factor(n), y = gamma_l1))+
  geom_boxplot(aes(color = penalty))+
  labs(title = paste("l1-error for gamma: BIC and pre-determined lambda \n for", M, "repetitions."),
       x = "Network size n",
       y = "l1-error")
```



